---
title: "Chicago Bulls 2019-20 Roster Targets"
author: "Andrew Mellor"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
     theme: tactile
     toc: true
     toc_depth: 3
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE, fig.align = 'center')
```

```{r  out.width = "20%"}
# Create the external file
htmltools::img(src = knitr::image_uri("figs/Chicago_Bulls_23.jpg"),
alt = 'logo',
style = 'width:1%',
style = 'position:absolute; top:0; right:0; padding:10px;')
````

# Scenario and Aim of this Data Analysis

In the most recent NBA season (2018-19), the Chicago Bulls placed 27th out of 30 (a 22-60 win-loss record), 19 wins from the playoffs. As a result the Bulls secured the #7 pick in the NBA draft lottery. 

The Bulls budget for player contracts 2019-20 is $118 million.  
The Portland Trailblazers have the biggest budget for 2019-20 with $148 million.  
The team with the best league record in 2018-19, the Milwaukee Bucks have a budget of $131 million. ^[Hoops Hype][Hoops Hype](https://hoopshype.com/salaries/)

**So this report will aim to find the best five starting players (positional information available at ^[Wikipedia][Wikipedia](https://en.wikipedia.org/wiki/Basketball_positions) the Bulls can afford. Ensuring we have enough budget leftover to have a full 12-man roster.**

*The Positions being:   
+Centre or 5  
+Power Forward or 4  
+Small Forward or 3  
+Shooting Guard or 2  
+Point Guard or 1  
 
## Load required packages
```{r Packages, message=FALSE, echo = TRUE}
#Include all required packages at the start
library(tidyverse) 
library(ggplot2)
library(broom)
library(readxl)
library(stringi)
library(knitr)
library(kableExtra)
```


## Data Source
Statistics from the 2018-19 NBA season. The original source for each set is also listed below:

1. 2018-19_nba_player_statistics.csv :  sourced from ^[basketball-reference.com][basketball-reference.com](https://www.basketball-reference.com/leagues/NBA_2019_totals.html)
2. 2018-19_nba_player-salaries.csv :  sourced from ^[hoopshype.com/salaries][hoopshype.com/salaries](https://hoopshype.com/salaries/)
3. 2019-20_nba_team-payroll.csv : sourced from ^[hoopshype.com/salaries][hoopshype.com/salaries](https://hoopshype.com/salaries/)
4. 2018-19_nba_team-statistics_1.csv : sourced from ^[basketball-reference.com][basketball-reference.com](https://www.basketball-reference.com/leagues/NBA_2019.html)
5. 2018-19_nba_team-statistics_2.csv : sourced from ^[basketball-reference.com][basketball-reference.com](https://www.basketball-reference.com/leagues/NBA_2019.html)


### Read in Data

```{r read} 
# read in the data sets from the working directory
statistics <-read_csv("data/2018-19_nba_player_statistics.csv")
salary <-read_csv("data/2018-19_nba_player-salaries.csv")
payroll <-read_csv("data/2019-20_nba_team-payroll.csv")
team_statistics_1 <-read_csv("data/2018-19_nba_team_statistics_1.csv")
team_statistics_2 <-read_csv("data/2018-19_nba_team_statistics_2.csv")
```

### Check the Data
```{r Structure, message=TRUE, echo = TRUE, results='hide'}
str(payroll) #provides structure
head(payroll) #shows first 6 rows
tail(payroll) #shows last 6 rows

str(salary) #provides structure
head(salary) #shows first 6 rows
tail(salary) #shows last 6 rows

str(statistics) #provides structure
head(statistics) #shows first 6 rows
tail(statistics) #shows last 6 rows

str(team_statistics_1) #provides structure
head(team_statistics_1) #shows first 6 rows
tail(team_statistics_1) #shows last 6 rows

str(team_statistics_2) #provides structure
head(team_statistics_2) #shows first 6 rows
tail(team_statistics_2) #shows last 6 rows
```


```{r Na, message=FALSE, echo = TRUE, results='hide'}
#Check for missing values
sum(is.na(payroll)) 
sum(is.na(salary)) 
#Looking at the data frame there are 4 columns without data, there are 576 players.
576*4
#we should remove the spare columns
sum(is.na(statistics)) 
which(is.na(statistics))
naniar::vis_miss(statistics)
#Looking at the data frame there are players with na for % results (2p%, 3p%, FT%) where they have not attempted a shot.
#there is no reason to remove these na's as they rpresent a non event.
sum(is.na(team_statistics_1)) 
which(is.na(team_statistics_1))
naniar::vis_miss(team_statistics_1)
#Looking at the data frame there are 3 columns without data, there are 30 teams.
30*3
#we should remove the spare columns
sum(is.na(team_statistics_2)) 
```

## Data Transformation

````{r Tidy Data}
#Removing unwanted data
salary <-salary[setdiff(colnames(salary), c('X4','X5', 'X6', 'X7'))]

team_statistics_1 <-team_statistics_1[setdiff(colnames(team_statistics_1), c('X23','X24', 'X25'))]

#We need to combine players that played for mutliple teams, using group_by "player_name" and summarise the columns that a numeric.
statistics <- statistics %>%
group_by(player_name, Pos) %>% 
summarise_each(funs(sum), 3:27)

#We should remove accents and periods from player names in the statistics data frame so it matches the salary data frame for later.
statistics$player_name <- statistics$player_name %>%
stringi::stri_trans_general("Latin-ASCII") %>%
stringr::str_replace_all(pattern = "\\.", replacement = "")

#Now we will also convert data that doesn't meet tidy data requirements (such as numbers at the start of variable names and %)
statistics <-rename(statistics,FGp = `FG%`, x3P = `3P`, x3PA = `3PA`, x3Pp = `3P%`, x2P = `2P`, x2PA = `2PA`, x2Pp = `2P%`, eFGp = `eFG%`, FTp = `FT%`)

team_statistics_1 <-rename(team_statistics_1, TSp = `TS%`, eFGp = `eFG%`, TOVp = `TOV%`, ORBp = `ORB%`, FTpFGA = `FT/FGA`, DRBp = `DRB%`)

team_statistics_2 <-rename(team_statistics_2,FGp = `FG%`, x3P = `3P`, x3PA = `3PA`, x3Pp = `3P%`, x2P = `2P`, x2PA = `2PA`, x2Pp = `2P%`,FTp = `FT%`)
````

## Exploratory Analysis
**Our most obvious observations should start with team offensive and defensive prowess, so these are the statistical areas we will focus on:**

*ORtg: Offensive Rating; An estimate of points produced (players) or scored (teams) per 100 possessions   
*DRtg : Defensive Rating; An estimate of points allowed per 100 possessions  
*NRtg: Net Rating; an estimate of point differential per 100 possessions  
*TOVp: Turnover Percentage; An estimate of turnovers committed per 100 plays.  


````{r Ratings and Wins}
ggplot(team_statistics_1, aes(x = ORtg, y = W))+ 
geom_point(alpha = 0.5, colour = "red")+
geom_smooth(method = "lm")

ggplot(team_statistics_1, aes(x = DRtg, y = W))+ 
geom_point(alpha = 0.5, colour = "red")+
geom_smooth(method = "lm")

ggplot(team_statistics_1, aes(x = NRtg, y = W))+ 
geom_point(alpha = 0.5, colour = "red")+ 
geom_smooth(method = "lm")

ggplot(team_statistics_1, aes(x = TOVp, y = W))+ 
geom_point(alpha = 0.5, colour = "red")+ 
geom_smooth(method = "lm")
````

**ORtg shows a positive correlation to wins, while DRtg and TOVp show a negative correlation. NRtg (Net Rating) an estimate of point differential per possessions shows what looks like the highest correlation.**

````{r Correlation}
#Checking the correlation between NRtg and Wins using the Perason method.
cor(x = team_statistics_1$NRtg, y = team_statistics_1$W, method = "pearson")
````


**Since both offensive (Offensive Rating) and defensive (Defensive Rating) measures play an important part in determining Net Rating and thus Wins we should look at a metric that measures most of these elements.** 

**The NBA provides and[Efficiency][Efficiency](https://en.wikipedia.org/wiki/Efficiency_(basketball), which is derived from basic individual statistics: points, rebounds, assists, steals, blocks, turnovers and shot attempts. The efficiency stat, in theory, accounts for both a player's offensive contributions (points, assists) and their defensive contributions (steals, blocks).**

**So if we take a look at those statistics to see if we get a linear relationship.**
````{r Stats & Net Rating}
team_statistics<- merge(team_statistics_1,team_statistics_2, by  = "Team")

team_statistics <- team_statistics %>%
  mutate(missed_FG = FGA - FG,
         missed_FT = FTA - FT)

statistics <- statistics %>%
  mutate(missed_FG = FGA - FG,
         missed_FT = FTA - FT)

ggplot(team_statistics, aes(x = PTS, y = NRtg))+ 
geom_point(alpha = 0.5, colour = "red") + 
geom_smooth(method = "lm")

ggplot(team_statistics, aes(x = TRB, y = NRtg))+
geom_point(alpha = 0.5, colour = "red") + 
geom_smooth(method = "lm")

ggplot(team_statistics, aes(x = AST, y = NRtg))+
geom_point(alpha = 0.5, colour = "red") + 
geom_smooth(method = "lm")

ggplot(team_statistics, aes(x = STL, y = NRtg))+
geom_point(alpha = 0.5, colour = "red") + 
geom_smooth(method = "lm")

ggplot(team_statistics, aes(x = BLK, y = NRtg))+
geom_point(alpha = 0.5, colour = "red") + 
geom_smooth(method = "lm")

ggplot(team_statistics, aes(x = FGA - FG, y = NRtg))+
geom_point(alpha = 0.5, colour = "red") + 
geom_smooth(method = "lm")

ggplot(team_statistics, aes(x = FTA - FT, y = NRtg))+
geom_point(alpha = 0.5, colour = "red") + 
geom_smooth(method = "lm")

ggplot(team_statistics, aes(x = TOV, y = NRtg))+
geom_point(alpha = 0.5, colour = "red") + 
geom_smooth(method = "lm")
````


```{r Data Transformation}
team_statistics <- team_statistics %>%
  mutate(EFF = PTS + TRB + AST + STL + BLK - (FGA - FG) - (FTA - FT) - TOV / G )

team_statistics <- team_statistics %>%
  mutate(EFF_per_game = EFF / G,
         PTS_per_game = PTS / G,
         REB_per_game = TRB / G,
         AST_per_game = AST / G, 
         STL_per_game = STL / G,
         BLK_per_game = BLK / G,
         missed_FG_per_game = missed_FG / G,
         missed_FT_per_game = missed_FT / G,
         TOV_per_game = TOV / G)
````


````{r Mutliple Linear Regression}
#Creating our linear model using lm.
fit <- lm(NRtg ~ PTS_per_game + REB_per_game + AST_per_game + STL_per_game + BLK_per_game, data = team_statistics)
tidy(fit, conf.int = TRUE)
````

Our slope coefficient says that teams that get 1 more:
*PTS_per_game than the average team, score 0.44 more NRtg_per_game than the average team  
*REB_per_game than the average team, score 0.48 more NRtg_per_game than the average team  
*AST_per_game than the average team, score 0.27 more NRtg_per_game than the average team  
*STL_per_game than the average team, score 0.11 more NRtg_per_game than the average team  
*BLK_per_game than the average team, score 1.44 more NRtg_per_game than the average team  

### Predicted Values
**Our model looks like:** 

**NRtg = -85.5 + PTS_per_game + REB_per_game + AST_per_game + STL_per_game + BLK_per_game**

## Assumptions
### 1. The response variable should be continuous (i.e. ratio/interval)
**NRtg (Net Rating) is a measure of an estimate of point differential per 100 possessions, so is ratio scale of measurement.**

### 2. There are two or more explanatory variables that are either continuous of categorical
**Each of our explanatory variables are continuous.**

### 3. Independence of Observations
**There should be independence of observations.**
```` {r Independence of Observations}
#Using the car package we can check for independoence of observations.
car::durbinWatsonTest(fit)
````
**The Durbin-Watson statistic for the model show: a value of 1.46, indicating that there is no correlation between the residuals and that we have independence of observations.**

### 4. Linearity
**There should be a linear relationship between the response variable (NRtg) and each explanatory variable.**
````{r Partial Regression Plots}
#use the car package to check for linear relationships by creating partial regression plots, accounting for the effect of the other explanatory variables and the respone against each explanatory variable.
car::avPlots(fit)
````
**We can see there is a linear relationship between the NRtg and each of our explanatory variable. STL_per_game is weak however.**

### 5. Outliers, Influential or High Leverage Points
**Outliers, Influential and/or high leverage points have the ability to influence our model, so there is a need to identify any and potentially remove them from the data.**
````{r Outliers}
#Check the data for outliers.
std_res <- rstandard(fit)
points <- 1:length(std_res)

ggplot(data = NULL, aes(x = points, y = std_res)) +
geom_point(colour = "black") +
ylim(c(-4, 4)) +
geom_hline(yintercept = c(-3, 3), colour = "black", linetype = "dashed")+
theme(panel.background = element_rect(fill = 'red'))
````

**There looks to be no outliers, beyond 3 standard deviations from 0, in fact all points are within 2 standard deviations from 0.**

````{r Leverage Points}
#Check to see if any of the potential outliers create leverage, using hatvalues.
hats <- hatvalues(fit)
hats_labels <- if_else(hats >= 0.4, paste(points), "")

ggplot(data = NULL, aes(x = points, y = hats)) +
geom_point(colour = "black") +
theme(panel.background = element_rect(fill = 'red'))+
geom_text(aes(label = hats_labels), nudge_x =1)
````

**There do not appear to be any leverage points as all hatvalues are closer to 0 than 1, although there are three points (6, 11, & 21) in particular that are above 0.4 that we should look at potentially investigating.**

````{r Cooks Distance}
#Check for influence on the linear regression by potential outliers.
cook <-cooks.distance(fit)
cook_labels <- if_else(cook >= 0.2, paste(points), "")

ggplot(data = NULL, aes(x =points, y = cook)) +
geom_point(colour = "black")+
theme(panel.background = element_rect(fill = 'red'))+
geom_text(aes(label = cook_labels), nudge_x =1)
````

**It does not appear that points 11 or 20 are showing any influence or leverage in this instance.**

````{r Cooks Distance2_PTS}
#We will double check each of the explanaotry variables against points 11 and 20 to see if we have any high leverage nad high influence.
ggplot(team_statistics, aes(x = PTS_per_game, y = NRtg))+
geom_point(alpha = 1, colour = "blue")+
geom_hline(yintercept = 0, colour = "red", linetype = "dashed")+
geom_smooth(method = "lm", colour = "blue")+
theme_gray()+
geom_text(aes(label = cook_labels), nudge_y = 0.5)
````
````{r Cooks Distance2_REB}
ggplot(team_statistics, aes(x = REB_per_game, y = NRtg))+
geom_point(alpha = 1, colour = "blue")+
geom_hline(yintercept = 0, colour = "red", linetype = "dashed")+
geom_smooth(method = "lm", colour = "blue")+
theme_gray()+
geom_text(aes(label = cook_labels), nudge_y = 0.5)
````

````{r Cooks Distance2_AST}
ggplot(team_statistics, aes(x = AST_per_game, y = NRtg))+
geom_point(alpha = 1, colour = "blue")+
geom_hline(yintercept = 0, colour = "red", linetype = "dashed")+
geom_smooth(method = "lm", colour = "blue")+
theme_gray()+
geom_text(aes(label = cook_labels), nudge_y = 0.5)
````
````{r Cooks Distance2_STL}
ggplot(team_statistics, aes(x = STL_per_game, y = NRtg))+
geom_point(alpha = 1, colour = "blue")+
geom_hline(yintercept = 0, colour = "red", linetype = "dashed")+
geom_smooth(method = "lm", colour = "blue")+
theme_gray()+
geom_text(aes(label = cook_labels), nudge_y = 0.5)
````
````{r Cooks Distance2_BLK}
ggplot(team_statistics, aes(x = BLK_per_game, y = NRtg))+
geom_point(alpha = 1, colour = "blue")+
geom_hline(yintercept = 0, colour = "red", linetype = "dashed")+
geom_smooth(method = "lm", colour = "blue")+
theme_gray()+
geom_text(aes(label = cook_labels), nudge_y = 0.5)
````
**Neither point 11 or 20 show high leverage or high influence.**

### 6. Homoscedasticity
**The data needs to show homoscedasticity.**
````{r Homoscedasticity}
#Plotting of the residuals against the fitted values.
res<- residuals(fit)
fitted <- predict(fit)


ggplot(team_statistics, aes(x = fitted, y = res))+
geom_point(colour = "black")+
geom_hline(yintercept = 0, colour = "black", linetype = "dashed")+
theme(panel.background = element_rect(fill = 'red'))+
geom_smooth(se = FALSE, colour = "white")

````
**This randomisation of the data shows homoscedasticity (constant variance), and as such we can be sure there appears to be no evidence of heteroscedasticity.**

### 7. Normality
**The residuals should be normally distributed.**
````{r Normality}
#Is there a normal distribution, check via a hitogram.

ggplot(data =NULL, aes(x= res))+
geom_histogram( colour = "red", fill = "black", binwidth = 2)+
theme(panel.background = element_rect(fill = 'red'))
````
**The data points appear normally distributed, although there is a larger tail.**

````{r Q-Q Plot}
#We can also check by using a nromal Q-Q plot.
ggplot(data = NULL, aes(sample =res))+
theme(panel.background = element_rect(fill = 'red'))+
stat_qq() + stat_qq_line()

````
**The Q-Q plot shows that the points appear normally distributed.**

### 8. Multicollinearity
**There should be no multicollinearity between the explanatory variables.**
````{r Pairs}
#We can check visually by using th pairs plot.
pairs(formula = ~ PTS_per_game + REB_per_game + AST_per_game + STL_per_game + BLK_per_game, data = team_statistics)
````
**There appears to be no evidence of a linear relationship between any of our explanatory variables.**

```` {r Variance Inflation Factor}
#Using the car packacge we can also check for multicollinearity.
car::vif(fit)

sqrt(car::vif(fit))
````
**The square root of the VIF shows how much greater the standard error in the relevant slope coefficient is, compared to if there was no relationship between predictors. e.g. PTS_per_game is 1.42 times larger than if there was a 0 correlation with the other explanatory variables.**

**This shows that there is no Multicollinearity.**

## Model Testing
**Our model that we are using is:**

**$NRtg = -85.5 + PTS_per_game + REB_per_game + AST_per_game + STL_per_game + BLK_per_game$**

### Applying the Model
````{r Applying the Model}
# Transform the data to create our Expected Net Rating (exp_NRtg_Per_game)
team_statistics<- mutate(team_statistics, exp_NRtg_per_game = predict(fit, newdata = team_statistics))

ggplot(team_statistics, aes(exp_NRtg_per_game, NRtg, label = Team)) + 
geom_point(colour = "black") +
geom_text(nudge_x = -1.25, cex = 2) +
theme(panel.background = element_rect(fill = 'red'))+
geom_abline(linetype = "solid", colour = "white") #Reference Line for 100% Prediction
````

### Wins
````{r Wins from NRtg}
ggplot(team_statistics, aes(x = W, y = exp_NRtg_per_game, label = Team)) + 
geom_point(colour = "black") +
geom_text(nudge_x = 3.5, cex = 2) +
theme(panel.background = element_rect(fill = 'red'))+
geom_abline(linetype = "dashed", colour = "blue")
````

## Player Metrics
**We calculate the number of minutes each team player per game on average across the league. Normally this would be 5 * 48 = 240 minutes, however there are games that go into overtime.**
```{r Team Minutes Summary}
min_per_game <- team_statistics %>%
group_by(Team) %>%
summarise(min_per_game = (MP/G)) %>%
pull(min_per_game) %>%
mean 

min_per_game
````


### Adjusting Players Expected Performance Per Minutes Played
**Next we can create new box score statistics per game, adjusted for average minutes played per game.**

````{r Per Minute Performance}
players <- statistics %>%
group_by(player_name) %>%
summarise(G = sum(MP) / min_per_game,
          PTS_per_game = sum(PTS) / G,
          REB_per_game = sum(TRB) / G,
          AST_per_game = sum(AST) / G, 
          STL_per_game = sum(STL) / G,
          BLK_per_game = sum(BLK) / G,
MP = sum(MP)) %>%
filter(MP >= 200) %>%
select(-G)
```` 

### Expected Net Rating Per Player
**The exp_NRtg metric can be interpreted as the net effect a player has on the overall score between their team and the opposition's team if all players are exactly like that player.**

````{r Expected NRtg Per Player}
players <- mutate(players, exp_NRtg = predict(fit, newdata = players))
````

````{r Expected NRtg Per Player ggplot}
players %>%
ggplot(aes(x = exp_NRtg)) +
geom_histogram(binwidth = 0.5, colour = "red", fill = "black")+
theme(panel.background = element_rect(fill = 'black'))
````

### Adding Salary & Position
```` {r Salary & Position}
players <- salary %>%
select(player_name, salary) %>% 
right_join(players, by = "player_name")

players <- statistics %>%
select(player_name, Pos) %>% 
right_join(players, by = "player_name")
````

### Selecting Players by Expected NRtg
````{r Expected NRtg}
players %>%
select(player_name, Pos, salary, exp_NRtg) %>% 
arrange(desc(exp_NRtg), salary) %>%
top_n(20)
````

````{r Expected NRtg ggplot}
players %>%
ggplot(aes(x = salary/1000000, y = exp_NRtg, color = Pos))+
geom_point()+ 
xlab("Salary (Millions)")+
theme(legend.position = "bottom")
````

## Players to Target

### Centre
````{r Expected NRtg ggplot Centre}
players %>%
filter(Pos == 'C-PF' | Pos == 'PF-C'| Pos == 'C') %>%
ggplot(aes(x = salary/1000000, y = exp_NRtg, color = player_name)) +
geom_point() + 
geom_text(aes(label=ifelse(exp_NRtg > 40,as.character(player_name),'')),hjust=1.2,vjust=0.5) +
theme(legend.position = "none")+
xlab("Salary (Millions)") 
````

**Joel Embiid & Anthony Davis are the two best Centres, however Karl-Anthony Towns shows tremendous value for money.**

### Power Forward
````{r Expected NRtg ggplot Power Forward}
players %>%
filter(Pos == 'C-PF' | Pos == 'PF-C' | Pos == 'PF' | Pos == 'PF-SF' | Pos == "SG-PF") %>%
ggplot(aes(x = salary/1000000, y = exp_NRtg, color = player_name)) +
geom_point() + 
geom_text(aes(label=ifelse(exp_NRtg > 35,as.character(player_name),'')),hjust=-0.05,vjust=0.5) +
expand_limits(x = 35)+
theme(legend.position = "none")+
xlab("Salary (Millions)") 
````

**Giannis Antetokounmpo is the best power forward in the league, his expected Net Rating is almost double the next best player, for $24million dollars, this may be worth the money.**

### Small Forward (Point Forward)
````{r Expected NRtg ggplot Small Forward}
players %>%
filter(Pos == 'PF-SF' | Pos == 'SF' | Pos == 'SF-SG' | Pos == "SG-SF") %>%
ggplot(aes(x = salary/1000000, y = exp_NRtg, color = player_name)) +
geom_point() + 
geom_text(aes(label=ifelse(exp_NRtg > 20,as.character(player_name),'')),hjust=1.1,vjust=0.5) +
theme(legend.position = "none")+
xlab("Salary (Millions)") 
````

**There is not many players at a value price here. We should target Kawhi Leonard.**

### Shooting Guard
````{r Expected NRtg ggplot Shooting Guard}
players %>%
filter(Pos == 'SG' | Pos == 'SG-SF' | Pos == 'PF-SG' | Pos == 'SG-SF') %>%
ggplot(aes(x = salary/1000000, y = exp_NRtg, color = player_name)) +
geom_point() + 
geom_text(aes(label=ifelse(exp_NRtg > 20,as.character(player_name),'')),hjust=-0.2,vjust=0.5) +
expand_limits(x = 30)+
  theme(legend.position = "none")+
xlab("Salary (Millions)") 
````

**Luka Doncic or Devin Booker should be our targets here.**

### Point Guard
````{r Expected NRtg ggplot Point Guard}
players %>%
filter(Pos == 'PG') %>%
ggplot(aes(x = salary/1000000, y = exp_NRtg, color = player_name)) +
geom_point() + 
geom_text(aes(label=ifelse(exp_NRtg > 20,as.character(player_name),'')),hjust=0,vjust=-1) +
expand_limits(x = 45, y = 75)+
theme(legend.position = "none")+
xlab("Salary (Millions)") 
````

**Ben Simmons or D'Angelo Russell should be our target here.**

# Chicago Bulls 2019-20

```{r Our Team}
starting_5 <- players %>%
filter(player_name %in% c("Karl-Anthony Towns", "Giannis Antetokounmpo", "Kawhi Leonard", "Luka Doncic", "D'Angelo Russell")) %>%
arrange(desc(salary))

View(starting_5)


starting_5 %>%
ggplot(aes(x = salary/1000000, y = exp_NRtg, label = player_name)) +
geom_point(colour = "black") +
geom_text(nudge_x = 4, cex = 3) +
theme(panel.background = element_rect(fill = 'red'))+
expand_limits(x = 37.5)+
theme(legend.position = "none")+
xlab("Salary (Millions)") 

sum(starting_5$salary)

kable(starting_5[1:5, 1:3]) %>%
  kable_styling("striped", full_width = F)%>%
  column_spec(1, bold = T)%>%
  row_spec(1:5, bold = T, color = "white", background = "#D7261E")
````

**Our starting team would cost $68,699,543. Leaving us approximately $50 million to secure the rest of the roster. **

**As a starting point, for the rest of the roster I would suggest Christian Wood as a backup Power Forward, he looks to be the most underpaid player in the league for his expected Net Rating. In addition to this if Ben Simmons can be signed for his salary that would give us 7 players for our roster for approximately $78 million, leaving us $40 million to fill the last 5 places.**

<center>
[](figs/Chicago_Bulls_logo.png){width=400px}
</center>

## References

